### 2021-07-21 paper.tex
first part of abstract added, needs more content

	% certificate page
	\section[certificate]{\hfill \Huge Certificate \hfill}
	\thispagestyle{empty}

	\pagenumbering{roman}

@@

	\section[abstract]{\hfill \Huge Abstract \hfill}

	This is going to be fun.
\end{document}

>>>>

	% certificate page
	\section[certificate]{\hfill \Huge Certificate \hfill}
	%\thispagestyle{empty}

	% roman page numbering
	\pagenumbering{roman}

@@

	% abstract
	\section[abstract]{}

	% reverting back to normal page numbering
	\pagenumbering{arabic}

	\thispagestyle{plain}
	\begin{center}
		\Large
		\textbf{Brain Tumor Detection}

		\vspace{0.4cm}
		\large
		Using various machine learning models to detect brain tumor.

		\vspace{0.4cm}
		\textbf{Authors}:

		\vspace{0.9cm}
		\textbf{Abstract}
	\end{center}

	Tumors are cancerous or non-cancerous mass or growth of abnormal cells in
	brain. Tumors can start in brain, or cancer elsewhere in the body can spread
	to brain. There are many way to control the occurrence of these abnormal
	cells. A tumor can be denoted as a malformed mass of tissues wherein the
	cells multiply abruptly and ceaselessly, that is there is no control over
	the growth of the cells.

	The process of Image segmentation is adopted for extracting abnormal tumor
	region within the brain. In the MRI (magnetic resonance image), segmentation
	of brain tissue holds very significant in order to identify the presence of
	outlines concerning the brain tumor. There is abundance of hidden
	information in stored in the Health care sector. With appropriate use of
	accurate data mining classification techniques, early prediction of any
	disease can be effectively performed.

	The project examines list of risk factors that are being traced out in brain
	tumor surveillance systems. Also the method proposed assures to be highly
	efficient and precise for brain tumor detection, classification and
	segmentation. To achieve this precise automatic or semi-automatic methods
	are needed. The project proposes an automatic segmentation method that
	relies upon CNN (Convolution Neural Networks), VGG 16 and Resent 50,
	determining small 7 x 7 kernels. By incorporating this single technique,
	segmentation and classification is accomplished. CNN (a ML technique) from
	NN (Neural Networks)wherein it has layer based for results classification.

\end{document}
